Centrality and Activity for Envolving Networks

### 2013-06-24 network-science/paper.tex

And we define the notation of some frequently used basic functions:
\begin{definition}
The adjacency matrix
\begin{equation}
A(G_t)=\begin{pmatrix}a_{ij}\end{pmatrix}_{n\times n},\text{ where }n=|V|,
a_{ij}\in \mathbb{R}^+,
\end{equation}
is the adjacency matrix of the graph at time $t$. More detailed
\begin{equation}
a_{ij}=\begin{cases}
0&(i=j)\\
\sum_{(i,j,t',w)\in E_t}w &(i<j)\\
a_{ji}&(i>j)
\end{cases}
\end{equation}
\end{definition}

@@

We then have
\begin{equation}
\left<k^\bullet\right>=2\left|E^\bullet\right|/\left|V\right|,
\end{equation}
where $\left|E^\bullet\right|/\left|V\right|$ only depends on the structure of
the network at a time spot. In many available online datasets, such as [?]%TODO
we can assume $\left<k^\bullet\right>$ is limited by a constant $K$, typically
$10^2$.
\definition Sparcity constant $K=\left<k^\bullet\right>$.

@@

The clustering coefficient[?], namely
\begin{equation}
c.c=\frac{\#\text{closed paths of len 2}}{\#\text{paths of len 2}},
\end{equation}
for a typical social network is a possitive
number, which means people are more willing to make interactions with close
related people than unfamiliars.

@@

If a vertex $v$ performs an interaction $(v,u)$ at time $t$, i.e., a new edge
is added to $G_t$, and suppose the interaction is the only change to the graph
at time $t$, then the activity of $v$ should be greater than if the edge is not
added.
\begin{equation}
E_t=E'_t\cup\{e(u,v,t,w)\}\implies \mathit{Act}(G_{t},v)>\mathit{Act}(G'_{t},v
).\label{eq-mono}
\end{equation}

>>>>

And we define the notation of some frequently used basic functions:
\begin{definition}
The adjacency matrix
\begin{equation}
A(G_t)=\begin{pmatrix}a_{ij}\end{pmatrix}_{n\times n},\text{ where }n=|V|,
a_{ij}\in \mathbb{R}^+,
\end{equation}
is the adjacency matrix of the graph at time $t$. More detailed
\begin{equation}
a_{ij}=\begin{cases}
0&(i=j)\\
\sum_{(i,j,t',w)\in E_t}w &(i<j)\\
a_{ji}&(i>j)
\end{cases}.
\end{equation}
Or, in case of directional graph,
\begin{equation}
a_{ij}=\begin{cases}
0&(i=j)\\
\sum_{(i,j,t',w)\in E_t}w &(i\neq j)
\end{cases}
\end{equation}
\end{definition}

@@

We then have
\begin{equation}
\left<k^\bullet\right>=2\left|E^\bullet\right|/\left|V\right|,
\end{equation}
where $\left|E^\bullet\right|/\left|V\right|$ only depends on the structure of
the network at a time spot. In many available online datasets,
we can assume $\left<k^\bullet\right>$ is limited by a constant $K$, typically
$10^2$.
\definition Sparcity constant $K=\left<k^\bullet\right>$.

@@

The clustering coefficient\cite{newman2010networks}, namely
\begin{equation}
c.c=\frac{\#\text{closed paths of len 2}}{\#\text{paths of len 2}},
\end{equation}
for a typical social network is a possitive
number, which means people are more willing to make interactions with close
related people than unfamiliars.

@@

If a vertex $v$ performs an interaction $(v,u)$ at time $t$, i.e., a new edge
is added to $G_t$, and the interaction is the only change to the graph
at time $t$, then the activity of $v$ should be greater than if the edge is not
added.
\begin{equation}
E_t=E'_t\cup\{e(u,v,t,w)\}\implies \mathit{Act}(G_{t},v)>\mathit{Act}(G'_{t},v
).\label{eq-mono}
\end{equation}
